Deep Learning

### 2015-01-12 deepreview.tex
Update deepreview.tex
Geoff removed two \cite{schmidreference}  and \cite{momentum}

From the earliest days of pattern recognition~\citep{selfridge,Rosenblatt57}
researchers aimed to replace hand-engineered features by multiple layers of
learned features.  This was eventually achieved by using the
backpropagation algorithm which was discovered independently by several
different groups in the 1970s and 1980s~\citep{Werbos74,Parker85,LeCun85,Rumelhart86b,schmidreference}.  
Backpropagation is simply an application of
the chain rule of derivatives (left of Figure~\ref{fig:backprop-box}),
which yields an efficient way of computing the gradient of a
smooth objective function with respect to all of the weights in a layered
network (Figures~\ref{fig:backprop-box} and~\ref{fig:mlp}). 
The objective function typically measures an error to be minimized: 
the discrepancy between
the actual output of the network on a given training case and the target
output for that case.  The key insight is that the error derivatives with
respect to the {\it outputs} of a layer can be computed by working
backwards from the error derivatives with respect to the outputs of the
subsequent layer. Once this backwards recursion has been used to compute
error derivatives for the outputs of all layers, it is easy to compute
error derivatives for the parameters (or weights) of each layer 
(Figure~\ref{fig:mlp}).

@@

Backpropagation provides an efficient way of computing gradients with respect to all of
the weights in a layered network on a single training case, but there are
still many ways to make use of these gradients. The most obvious method is
to average the gradients over all of the cases in the training set and then
to change each weight in proportion to its negative gradient, which is the
direction where a small change will most improve the objective function. 
When the training set contains millions of cases and is highly redundant
% explaining what ``redundant'' means, here
(with many examples illustrating variations of the same underlying 
aspect or concept), however,
this is needlessly slow. It is much faster to compute the average gradient
on a small ``mini-batch'' of randomly chosen training cases and to update
each weight by this stochastic estimate of its full gradient, times a
learning rate which decays as learning proceeds. Stochastic gradient
descent can be improved by using the history of the individual weight
gradients to adapt the learning rate for each weight~\citep{bottou-bousquet-2008-small}
or to provide additional increments that depend on earlier gradients~\citep{momentum}
but these techniques are still the subject of controversy and are beyond
the scope of this review (but see~\citet{Montavon2012} for tricks of the trade). 
However, it is now widely accepted that some
form of stochastic gradient descent is the best bet for large, redundant
datasets.

>>>>

From the earliest days of pattern recognition~\citep{selfridge,Rosenblatt57}
researchers aimed to replace hand-engineered features by multiple layers of
learned features.  This was eventually achieved by using the
backpropagation algorithm which was discovered independently by several
different groups in the 1970s and 1980s~\citep{Werbos74,Parker85,LeCun85,RHW}.  
Backpropagation is simply an application of
the chain rule of derivatives (left of Figure~\ref{fig:backprop-box}),
which yields an efficient way of computing the gradient of a
smooth objective function with respect to all of the weights in a layered
network (Figures~\ref{fig:backprop-box} and~\ref{fig:mlp}). 
The objective function typically measures an error to be minimized: 
the discrepancy between
the actual output of the network on a given training case and the target
output for that case.  The key insight is that the error derivatives with
respect to the {\it outputs} of a layer can be computed by working
backwards from the error derivatives with respect to the outputs of the
subsequent layer. Once this backwards recursion has been used to compute
error derivatives for the outputs of all layers, it is easy to compute
error derivatives for the parameters (or weights) of each layer 
(Figure~\ref{fig:mlp}).

@@

Backpropagation provides an efficient way of computing gradients with respect to all of
the weights in a layered network on a single training case, but there are
still many ways to make use of these gradients. The most obvious method is
to average the gradients over all of the cases in the training set and then
to change each weight in proportion to its negative gradient, which is the
direction where a small change will most improve the objective function. 
When the training set contains millions of cases and is highly redundant
% explaining what ``redundant'' means, here
(with many examples illustrating variations of the same underlying 
aspect or concept), however,
this is needlessly slow. It is much faster to compute the average gradient
on a small ``mini-batch'' of randomly chosen training cases and to update
each weight by this stochastic estimate of its full gradient, times a
learning rate which decays as learning proceeds. Stochastic gradient
descent can be improved by using the history of the individual weight
gradients to adapt the learning rate for each weight~\citep{bottou-bousquet-2008-small}
or to provide additional increments that depend on earlier gradients 
but these techniques are still the subject of controversy and are beyond
the scope of this review (but see~\citet{Montavon2012} for tricks of the trade). 
However, it is now widely accepted that some
form of stochastic gradient descent is the best bet for large, redundant
datasets.
